Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-06-09 WSSSPE1_report/WSSSPE1_summary_report.tex
fixing spelling, small change

It appears that while some of the basics of computing may be
similar, the tools commonly used for computing have changed quite
significantly. Reference was made to Perl, which was commonly used,
giving way to whole new languages, such as Python, for gluing things
together and how this induces many students into entirely rewriting
the scaffolding, leaving the old to rot and the experiments to become
non-reproducible as the tools change. There was discussion of this
tendency along with the enormous differences in the speed and ease of
sharing---having to ship tapes around (GCC, Emacs, etc) as opposed to
the immediate sharing of the latest development online, using revision
control systems like CVS, Subversion, Git, Mercurial, Bazaar, etc.

>>>>

It appears that while some of the basics of computing may be
similar, the tools commonly used for computing have changed quite
significantly. Reference was made to Perl, which was commonly used,
giving way to whole new languages, such as Python, for gluing things
together and how this induces many students into entirely rewriting
the scaffolding, leaving the old to rot and the experiments to become
non-reproducible as the tools change. There was discussion of this
tendency along with the enormous differences in the speed and ease of
sharing---having to ship tapes around in the early days of software development
(which shaped development of GCC and Emacs in their formative years) as opposed to
the immediate sharing of the latest development online, using revision
control systems like CVS, Subversion, Git, Mercurial, Bazaar, etc.
